Order reduction and MILP models for real-time DNN robustness certification.

### 2025-11-11 CAV 2026/experiments.tex
Add CAV2026 folder
try
1000s
sentences

@@

1v, $500$ & $1.412$ & $.161$ & .057 \\\hline 
3v, $1000$ & {\bf 1.137} & $.103$ & $.065$\\\hline 
2v, $1000$ &  $1.182$ & $.084$& {\bf .084}  \\\hline\hline

>>>>

\subsection{Global Robustness Comparison vs Vhagar and ITNE}

To be able to compare with Vhagar, we have to use Vhagar benchmarks: 
perturbation they consider (here $L_\infty=0.05$) on their DNNs (here Conv1 for MNIST, FMNIST and CIFAR-10), for which the reduction rules of integer variables are implemented. We test with 1000s Time-Out, as well as one test with 14400s time out, showing that much longer time-out does not have a big impact on the result.

\begin{table}[h!]
	\centering
	\begin{tabular}{||c|c|c|c|c||}\hline\hline
	Benchmark & model &        Bound $\downarrow$ &  Sol. &      Worst-Case $\uparrow$ \\\hline \hline
	MNIST   & Vhagar &  & & 
    \\
	M-Conv1 & ITNE &  & & 
	\\ 
    TO=1000s & 2v &   & & 
    \\\hline

	FMNIST & Vhagar &  ? &  ? & ? 
    \\
	F-Conv1  & ITNE &  $29.17$ &  $22.55$ & $22.55$
	\\ 
    TO=1000s & 2v &  {\bf 23.08} &  $23.02$ &  $23.02$ 
    \\\hline

	FMNIST & Vhagar &  $37.01$ &  $22.06$ & $22.06$ 
    \\
	F-Conv1  & ITNE &  $29.17$ &  $22.55$ & $22.55$
	\\ 
    TO=14400s & 2v &    {\bf 22.84} &  $22.53$ &  $22.53$ 
    \\\hline

	CIFAR-10  & Vhagar &  & & 
    \\
	C-Conv1  & ITNE &  & & 
	\\ 
    TO=1000s & 2v &    & & 
    \\\hline \hline

     \end{tabular}
	\caption{Comparison with Vhagar for $L_\infty=0.05$ perturbation.}
    \label{table.classical}
\end{table}

@@

1v, $500$ & $1.412$ & $.161$ & .057 \\\hline 
3v, $1000$ & {\bf 1.137} & $.103$ & $.065$\\\hline 
2v, $1000$ &  $1.182$ & $.084$& {\bf .084}  \\\hline
ITNE, $1000$ &  $1.371$ & $.085$& {\bf .085}  \\\hline\hline
